Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce

### 2019-09-26 Paper.tex
dasddas

In this paper we present a MapReduce runtime system as a solution to these problems. Although job's execution using our system requires more resources respect to other implementations due to process replications, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
\end{abstract}

\keywords{MapReduce, Arbitrary Fault Tolerance, Locality Awareness, Speculative Execution, Leader Election Algorithm, Deferred Execution}
\maketitle

@@

In order to enable communication with the Internet and therefore allow a local computer to connect to our system, we have adopt AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} which able us to associate to some of our EC2 instance to a public static IPv4 addresses\footnote{Public IPv4 addresses associated to any EC2 instances by default change after every start. Therefore, if an Amazon EC2 crashed and have to be restarted, client wouldn't able to connect to it due to address change.}.

Observe that processes are not all the same but several kind of these exist, with its own features and aims: although we will describe them in detail in following section, just note that we distinguish three process type: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);

Note that our MapReduce system is been implemented to execute word-count job only. We have built our system from scratch using Go programming language\footnote{\url{https://golang.org}} using some external libraries, which are all reported in table \ref{tab:libraries}.

@@

It can interact with system's key-value storage service (i.e. DFS or an equivalently cloud key-value storage service) for job's input uploading and job's output downloading. To perform data transmissions, client processes use HTTP-based RESTful APIs, according to which both an URL and standard HTTP methods (\texttt{GET} and \texttt{PUT}) only are required.

@@

However unlike Apache Hadoop framework, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}. Therefore, to ensure an high system availability, inspired by Apache Mesos\textsuperscript{TM}\ architecture\footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, we have adopt a design according to which multiple PP backup copies exist and they run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by. Using this approach, is possible to manage a PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.

@@

Therefore we have adopt a design according to which LPP save its state regularly. Since LPP state consists on a very small amount of data, we have design LPP to store its state into Apache Zookeeper cluster upon the occurrence of certain events. When a LPP crash failure occurs, the new leader can easily retrieves last saved state from  ZooKeeper cluster. Note that Apache Zookeeper's processes is been replicated too in order to tolerate a certain number of faults upon Zookeeper cluster.

Another very important aspect of PP is its ability to recognize duplicated requests coming from client; adopting a \textit{most-once semantics}, LPP is able to recognize duplicates re-forwarding its reply to client while client process, if it detects that LPP is been crashed, it will forward a query to Zookeeper cluster in order to know who is the new LPP. Note that WP too are designed according to most-once semantics.

Another difference with Hadoop \textit{JobTracker} process regards task scheduling approach. In our design LPP schedules tasks to WP using a \textit{push-based} approach, contrariwise Hadoop JobTracker schedules task using a \textit{pull-based} approach where WP ask for tasks\cite{LARTS}.

@@

To achieve fault tolerance we have adopt a design according to which each task is executed more than once by different processes running on different host. To do this, as you can see from figure \ref{fig:model}, we have adopt a design according to which all worker processes are organized in several groups which we have used to mask one or more faulty processes: these groups are called \textit{Worker Processes Group} (WPG). To be more precise, an WPG is a set of identical WP, each of which execute \textit{the same commands using the same input data in the same order}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs.

@@

Clearly, this design require more resources respect to classic MapReduce scheme: to tolerate at most $f$ arbitrary failures, each WPG have to contains at least $2f+1$ different WPs, therefore a total of $n(2f+1)$ different WPs are required (to which is also added a certain number of PPs run on different machine).

Although its very high costs, this design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs. If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG (increasing the number of PP backups too).

@@

At this point high costs of this solution should be clear to reader because everything is replicated $2f + 1$ times as map/reduce task, data transmissions and so on. Can we have a good level of fault tolerance without worsening performance? How can we do AFT-Map Task and AFT-Reduce Task efficiently?

In this section we will explain a set of solutions and techniques which we have adopt in our system to reduce costs and do things efficiently:

@@

Since outputs computed by WPs can be very large, we have adopted an approach according to which, instead of to compare raw data, LPP fetches and compares \textit{digests} that is fixed size strings obtained from WPs outputs using an hash function. The main advantage of this technique is that digest size are many times smaller than task's data output, allowing us to validate task's output reducing network traffic among servers.

@@

Waiting for $2f + 1$ matching replies during any AFT Map-Task/AFT-Reduce Task can be a waste of time especially when no faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ replicas for a given AFT-Map Task/AFT-Reduce Task.

Therefore, to minimize both the number of replicas executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware Deferred Execution}.

@@

We have designed our task scheduler to be also \textit{state-aware} since priority is given to those WPs whit minimum CPU utilization which we compute using \texttt{mpstat} tool. WP's state is acquired indirectly by LPP through their replies.

@@

Although the advantages of the deferred execution mechanism describes above, we believe that waiting for $f + 1$ matching digest for all AFT Map-Tasks before starting the Reduce-Phase can worsen the time for the job completion, especially when WPs arbitrary failures are uncommon. Remember that, assuming that we have $n$ WPGs, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies; all Map-Phase may require long time due, for instance, to network traffic or big  data-set.

A way to increase system's performance reducing its response time is the following: when all $n$ scheduled AFT Map-Tasks have received the \textit{first} replica's result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finish. Essentially, our system make a bet according to which arbitrary faults are highly unlikely therefore first Map-Task replies are considered as correct. This mechanism is known in literature called \textit{Speculative Execution}, an optimization technique applied frequently in computer technology.

@@

So far we have not yet mentioned the shuffle task according to which WP redistribute data (produced by the map function), such that all data belonging to one key is located on the same WP's node. Unlike Hadoop implementation, shuffle task is difficult and expensive due to process replication and to optimization technique described so far. Clearly, due to process replication, data transfers among servers are replicated too, generating an huge amount of network traffic. Evidently, when large data set are involved, move data repeatedly among server became a bottleneck.

Therefore we have adopted a design aware of data locations capable to reduce the overall amount of transferred data: this approach is called \textit{Data-Locality-Aware Reduce Scheduling}. That solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}"; in other words  "\textit{moving computation towards data is cheaper than moving data towards computation}".

Using the same Hadoop terminology, map task output, produces by every WPs, are called \textit{partition} and, contrary to splits, they are of variable sizes: so why not just shuffle smaller partitions instead big one? Then, why not schedule a AFT-Reduce Task to the WPG which nodes has bigger partition? In this way we can avoid transferring huge amount of data increasing overall system performances.

To explain how our scheduler works, let's illustrate an example: assume for simplicity to have only two WPGs $\lbrace g_1, g_2 \rbrace$. Let $P_{i:g_i}$ the partition owned by WPG $g_i$ which contains all key-value pairs which must be submitted to reduce task $R_i$. Suppose that $P_{1:g_1}$, $P_{2:g_1}$, $P_{1:g_2}$ and $P_{2:g_2}$ have a size of 300 MB, 150 MB, 150 MB and 300 MB respectively. In this context LPP schedules $R_1$ to $g_1$ and $R_2$ to $g_2$ because in this way is able to reduce transferred data among WPGs by 50\%. In other words, LPP is design to schedule AFT-Reduce Tasks reducing overall amount of shuffled data.

>>>>

In this paper we present a MapReduce runtime system as a solution to these problems. Although job's execution using our system requires more resources respect to other implementations due to process replication, we believe that this cost is acceptable for critical applications that require an higher level of fault tolerance.
\end{abstract}

\keywords{MapReduce, Arbitrary Fault Tolerance, Data-Locality Awareness, Speculative Execution, Leader Election Algorithm, Deferred Execution}
\maketitle

@@

In order to enable communication with the Internet and therefore allow a local computer to connect to our system, we have adopt AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} which able us to associate to some of our EC2 instance to a public static IPv4 addresses.

Observe that processes are not all the same but several kind of these exist, with its own features and aims: although we will describe them in detail in following section, just note that we distinguish three process types: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);

Note that our MapReduce system, capable to execute word-count job only, is been implemented from scratch using Go programming language\footnote{\url{https://golang.org}} using some external libraries, which are all reported in table \ref{tab:libraries}.

@@

It can interact with a key-value storage service (i.e. DFS or an equivalently cloud key-value storage service) for job's input uploading and job's output downloading. To perform data transmissions, client processes use HTTP-based RESTful APIs, according to which both an URL and standard HTTP methods (\texttt{GET} and \texttt{PUT}) only are required.

@@

However unlike Apache Hadoop framework, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that PP, and the host where it is running, may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}. Therefore, to ensure an high system availability, inspired by Apache Mesos\textsuperscript{TM}\ architecture\footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, we have adopt a design according to which multiple PP backup copies exist and they run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by. Using this approach, is possible to manage a PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.

@@

Therefore we have adopt a design according to which LPP saves its state regularly. Since LPP state consists on a very small amount of data, we have design LPP to store its state into Apache Zookeeper cluster upon the occurrence of certain events. When a LPP crash failure occurs, the new leader can easily retrieves last saved state from  ZooKeeper cluster. Note that Apache Zookeeper's processes is been replicated too in order to tolerate a certain number of faults upon Zookeeper cluster.

Another very important aspect of PP is its ability to recognize duplicated requests coming from client (which can retransmitt a same request) re-forwarding responses; in other words, we have adopt a \textit{most-once semantics}. Note that WP too are designed according to most-once semantics.

Another difference with Hadoop \textit{JobTracker} process regards task scheduling approach. In our design LPP schedules tasks to WP using a \textit{push-based} approach, contrariwise Hadoop JobTracker schedules task using a \textit{pull-based} approach where WPs ask for tasks\cite{LARTS}.

@@

To achieve fault tolerance we have adopt a design according to which each task is executed more than once by different processes running on different host. To do this, as you can see from figure \ref{fig:model}, all worker processes has been organized in several groups which we have used to mask one or more faulty processes: these groups are called \textit{Worker Processes Group} (WPG). To be more precise, an WPG is a set of identical WP, each of which execute \textit{the same commands using the same input data}; therefore we expected that all WPs belonging to a same group would produce the same output when no arbitrary fault occurs.

@@

Clearly, this design requires more resources respect to classic MapReduce scheme: to tolerate at most $f$ arbitrary failures all WPGs have to contain at least $2f+1$ different WPs, therefore a total of $n(2f+1)$ different WPs is required.

Although its very high costs, this design is scalable in several ways: if the number of users or data input size grows, it should be possible to extend the system, at reasonable cost, adding more WPGs. If we want an higher level of arbitrary fault-tolerance, we should add more WP to each WPG.

@@

At this point should be clear to reader that our design, despite its simplicity, is very expensive because almost everything is replicated $2f + 1$ times like map/reduce tasks, data transmissions and so on. Can we have a good level of fault tolerance without worsening performance? How can we do AFT-Map Task and AFT-Reduce Task efficiently?

In this section we will explain a set of solutions and techniques which we have adopt in our system to optimize it reducing costs and doing things efficiently.

@@

Since outputs computed by WPs can be very large, we have adopted an approach according to which, instead of to compare raw data, LPP fetches and compares \textit{digests}, that is fixed size strings obtained from raw data outputs using an hash function. The main advantage of this technique is that digest size are many times smaller than task's data output, allowing us to validate task's output reducing network traffic among servers.

@@

It is frequently a good idea to distinguish between the most common case and the worst possible case and treat them differently. In our system the occurrence of $f$ arbitrary faults represents the worst possible case, not the common in which less than $f$ errors occur. To improve considerably system's performance is important to make the common case fast. When worst case occurs, is sufficient to make it correct.

Therefore waiting for $2f + 1$ matching replies during any AFT-Map Task/AFT-Reduce Task can be a waste of time especially when fewer faults occur or we have already received a sufficient number of reply to establish the output's correctness; in other words, we believe that there is no point in always executing $2f + 1$ replicas for a given AFT-Map Task/AFT-Reduce Task.

Therefore, to minimize both the number of replicas executed and the overhead due to network traffic, we have adopted a mechanism that we have called \textit{Locality-Aware-And-State Deferred Execution}.

@@

We have designed our task scheduler to be also \textit{state-aware} since priority is given to those WPs which have minimum CPU utilization which we compute using \texttt{mpstat} tool. WPs states are acquired indirectly by LPP through their replies.

@@

Although the advantages of the deferred execution mechanism describes above, we believe that waiting for $f + 1$ matching digest for all AFT Map-Tasks before starting the Reduce-Phase can worsen the time for the job completion in some situations. Assuming that we have $n$ WPGs, since we need at least $f + 1$ matching reply from each WPG, we have to wait for at least $n(f + 1)$ replies to fully complete Map-Phase, which may require long time.

A way to increase system's performance reducing its response time is the following: when all $n$ scheduled AFT Map-Tasks have received the \textit{first} replica's result, LPP starts Reduce-Phase immediately without waiting for each AFT Map-Tasks receive exactly $f + 1$ matching results; in other words, Reduce-Phase starts after one replica of all AFT Map-Tasks finishes. Essentially, our system make a bet according to which arbitrary faults are highly unlikely and therefore first Map-Task replies can be considered as correct. This mechanism is known in literature \textit{Speculative Execution}, an optimization technique applied frequently in computer technology.

@@

So far we have not yet mentioned the shuffle task according to which WP redistribute data (produced by the map function), such that all data belonging to one key is located on the same WP's node. Unlike Hadoop implementation, shuffle task is difficult and expensive due to processes replication. Clearly data transfers among servers have to be replicated, generating an huge amount of network traffic and evidently, when large data set are involved, move data repeatedly among server became a bottleneck.

Therefore we have adopted a design aware of data locations capable to reduce the overall amount of transferred data: this approach is called \textit{Data-Locality-Aware Reduce Scheduling}. That solution is based on a basic principles which states that "\textit{moving computation towards data is cheaper than moving data towards computation}".

Using the same Hadoop terminology, map task output, produces by every WPs, are called \textit{partition} and, contrary to splits, they are of variable sizes: so why not just shuffle smaller partitions instead big one? Then, why not schedule an AFT-Reduce Task to the WPG which nodes has bigger partition? In this way we can avoid transferring huge amount of data increasing overall system performances.

To explain how our scheduler works, let's illustrate it with an example: assume for simplicity to have only two WPGs $\lbrace g_1, g_2 \rbrace$. Let $P_{i:g_i}$ the partition owned by WPG $g_i$ which contains all key-value pairs which must be submitted to reduce task $R_i$. Suppose that $P_{1:g_1}$, $P_{2:g_1}$, $P_{1:g_2}$ and $P_{2:g_2}$ have a size of 300 MB, 150 MB, 150 MB and 300 MB respectively. In this context LPP schedules $R_1$ to $g_1$ and $R_2$ to $g_2$ because in this way is able to reduce transferred data among WPGs by 50\%.
